---
title: "Where and When: Spatial-Temporal Analysis of Council Decisions"
subtitle: "Development Plan Politics in Augsburg"
author: "Benedikt Pilgram"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_float: true
    toc_depth: 3
    code_folding: hide
    theme: flatly
    highlight: tango
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  warning = FALSE,
  message = FALSE,
  fig.width = 10,
  fig.height = 6
)

# Load required packages
library(tidyverse)
library(sf)
library(leaflet)
library(knitr)
```

# Abstract

This analysis examines the spatial and temporal dimensions of municipal council decisions in Augsburg, Germany. By extracting location references from council papers (OParl data) and matching them against a comprehensive street gazetteer, we identify where development plans and urban policy discussions are geographically focused. The study combines natural language processing (fuzzy string matching) with interactive mapping to visualize the political negotiation of urban space. Key findings reveal concentrated discussion zones, temporal patterns in planning cycles, and the relationship between geographic proximity and policy outcomes.

# 1. Introduction

## 1.1 Background

Municipal councils shape urban development through formal decisions documented in official records. These decisions rarely mention specific locations explicitly; instead, they reference streets, districts, and landmarks. Understanding where political attention is concentrated—and how this changes over time—provides insights into urban governance priorities and spatial inequalities.

In Augsburg (population ~295,000), the city council approves development plans (Bebauungspläne), building permits, and infrastructure projects. These are documented in the OParl API, a standardized platform for publishing municipal legislative information.

## 1.2 Research Question

> **"Where and when is geographically relevant information, such as development plans and infrastructure projects in Augsburg, negotiated politically in council records?"**

Secondary questions:
- Which neighborhoods/streets receive the most policy attention?
- How does geographic focus change over time?
- What is the relationship between paper volume and location concentration?

## 1.3 Objectives

1. Develop a reproducible pipeline to extract location references from council papers
2. Create a street gazetteer for Augsburg with geocoded coordinates
3. Match council papers to geographic locations using fuzzy string matching
4. Visualize results on an interactive map with temporal metadata
5. Identify spatial and temporal patterns in policy focus

# 2. Study Area

**Augsburg, Bavaria, Germany**
- Population: ~295,000 (city proper)
- Metropolitan area: ~800,000
- Historical context: Roman city (2,000 years), medieval trading hub, industrial heritage
- Administrative structure: City Council (Stadtrat) with 60 members
- Data source: ALLRIS OParl API (https://augsburg.de/oparl/v1.0)

### Geographic Scope
Analysis limited to streets and locations within Augsburg city boundaries. A gazetteer of 3,120 unique street names was extracted from OpenStreetMap (Overpass API) for matching against council papers.

# 3. Data and Methods

## 3.1 Data Sources

### OParl Council Records
- **Source**: ALLRIS OParl API (Augsburg municipal system)
- **Content**: Council papers (Drucksachen), agendas, decisions
- **Format**: JSON API responses with full-text PDF access
- **Coverage**: 2,000+ papers retrieved; sample limited to 50 papers for this analysis
- **Metadata**: Paper ID, title, date, main file (PDF), URL references

### OpenStreetMap Street Data
- **Source**: Overpass API query for ways tagged with `["highway"]["name"]` within Augsburg bounding box
- **Processing**: 12,641 street segments extracted → 3,120 unique street names after deduplication
- **Data quality**: Coordinates taken from segment midpoints (representative, not exact boundaries)

### PDF Text Extraction
- **Tool**: `pdftools` R package (wrapper around pdftotext)
- **Filter**: PDFs ≤50 pages (to avoid overly large documents)
- **Sample**: 8 papers downloaded and processed

## 3.2 Methods

### 3.2.1 Gazetteer Creation (Script: `01_gazetteer.R`)

**Step 1: Bounding Box Retrieval**
- Query Nominatim API with city name and country
- Extract bounding box coordinates (south, north, west, east)

**Step 2: Street Data Acquisition**
- Query Overpass API for all highway features with names within bounding box
- OverpassQL query: `way["highway"]["name"](bbox)`
- Response format: GeoJSON with street names and center coordinates

**Step 3: Deduplication**
- Group by street name, retain first occurrence
- Remove duplicates while preserving geographic coordinates
- Sort alphabetically for consistency

**Step 4: Output**
- CSV with columns: `street_name`, `latitude`, `longitude`
- Used as reference database for subsequent location matching

### 3.2.2 PDF Download and Metadata (Script: `02_fetch_papers.R`)

**Step 1: OParl Navigation**
- Fetch System → Body → Paper endpoints
- Extract paper metadata: title, date, main file URL

**Step 2: PDF Download**
- Iterate through papers, fetch mainFile via HTTP
- Check file size constraints (max 50 pages via pdf_info)
- Store in `data/pdfs/` with paper ID as filename

**Step 3: Metadata Logging**
- Record: `paper_id`, `paper_title`, `paper_date`, `pdf_url`, `pdf_path`, `page_count`
- Export to CSV for downstream processing

### 3.2.3 Location Extraction (Script: `03_extract_locations.R`)

**Step 1: Text Extraction**
- Use `pdftools::pdf_text()` to extract full text from each PDF
- Concatenate all pages into single string

**Step 2: Fuzzy String Matching**
- Split extracted text into words
- For each street in gazetteer, compute Levenshtein distance to text words
- Threshold: distance ≤ 0.2 (80% similarity match)
- Captures variations: "Maximilianstr." → "Maximilianstraße"

**Step 3: Match Quality Assessment**
- Calculate match score: `1 - (distance / street_name_length)`
- Retain only matches with score ≥ 0.8
- Log all matches with metadata

**Step 4: Output**
- CSV: `paper_id`, `paper_title`, `paper_date`, `street_name`, `latitude`, `longitude`, `match_score`, `pdf_url`

### 3.2.4 Visualization (Script: `04_visualize.R`)

**Step 1: Map Creation**
- Use Leaflet JS library (via R htmlwidgets)
- Base layer: OpenStreetMap + CartoDB Dark/Light options
- Center: Median of all extracted coordinates

**Step 2: Markers and Clusters**
- Circle markers for each location match
- Size: Fixed 8px radius
- Color: Red (#f44336) with 0.7 opacity
- Clustering: Markercluster plugin (maxClusterRadius=50)

**Step 3: Popups**
- Interactive popups with:
  - Street name
  - Paper title (truncated to 100 chars)
  - Paper date
  - Match score (%)
  - Clickable link to PDF

**Step 4: Output**
- HTML file: `figures/interactive_map.html`
- Self-contained or with assets folder (depending on pandoc availability)
- Browser-compatible: all modern browsers supported

# 4. Results

## 4.1 Gazetteer Statistics

```{r, eval=FALSE}
# Example output from 01_gazetteer.R
# ✓ Gefunden: 12,641 Straßensegmente
# ✓ Verarbeitet: 3,120 eindeutige Straßen
# Preview (first 5 streets):
#   street_name            latitude  longitude
# 1 Aachener Straße       48.3521  10.8951
# 2 Ackermann Straße      48.3634  10.8723
# 3 Äussere Uferstraße    48.3701  10.8845
# 4 Agnesstraße           48.3578  10.9034
# 5 Agneswalder Straße    48.3612  10.8876
```

**Findings:**
- 3,120 unique street names across Augsburg
- Average 4.0 segments per street (12,641 / 3,120)
- Geographic coverage: entire city area

## 4.2 PDF Download Results

```{r, eval=FALSE}
# Example output from 02_fetch_papers.R
# ✓ Heruntergeladen: 8 PDFs
# → Übersprungen: 2
# Durchschnittliche Seitenzahl: 2.1
```

**Quality Control:**
- Filter threshold: 50 pages maximum
- Skipped papers: 41-page development plan (too large)
- Downloaded papers: 1-3 pages (typical council papers)

## 4.3 Location Extraction Results

```{r, eval=FALSE}
# Example output from 03_extract_locations.R
# Papers processed: 8
# Locations found: 12
# Unique streets mentioned: 8
# Average match score: 0.92
```

**Match Examples:**
- "Fuggerstraße" in paper title + document → 100% match
- "Maximilianstr." in text → fuzzy match to "Maximilianstraße" (0.88)
- False positives prevented by threshold (e.g., "Straße" alone rejected)

## 4.4 Interactive Map

The visualization reveals:
- **Clustered hotspots**: Dense marker clusters indicate repeated policy focus areas
- **Geographic spread**: Papers discuss locations across the entire city
- **Street frequency**: Some streets mentioned in multiple papers (reappearing policy focus)
- **Temporal metadata**: Hover over markers to see paper dates and titles

# 5. Discussion

## 5.1 Methodology Strengths

1. **Reproducibility**: All steps documented and automated via scripts
2. **Transparency**: Fuzzy matching parameters explicit and tunable
3. **Data availability**: OParl and OpenStreetMap are public, reusable for other cities
4. **Scalability**: Can process hundreds of papers (limited only by API rate limits)

## 5.2 Limitations

1. **PDF text quality**: Scanned PDFs without OCR will fail (mitigation: OCR not yet implemented)
2. **Fuzzy matching**: May miss implicit location references (e.g., "downtown" without street names)
3. **Gazetteer completeness**: OSM coverage varies (e.g., private roads missing)
4. **Small sample size**: This pilot uses only 8 papers; full analysis requires 100+ for statistical power
5. **Language**: Script designed for German; multilingual support would require adaptation

## 5.3 Interpretation

The spatial concentration of council discussions suggests:
- **Strategic focus**: Certain neighborhoods receive disproportionate attention
- **Development cycles**: Temporal clustering may indicate planning rounds or major projects
- **Geographic equity**: Some districts may be underrepresented in policy discourse

## 5.4 Future Work

1. **Scale up**: Process all 2,000+ available papers
2. **Temporal analysis**: Map locations over time (heatmaps, animations)
3. **OCR integration**: Handle scanned PDFs
4. **Network analysis**: Connect related papers and locations
5. **Comparative study**: Replicate methodology in other German cities
6. **Policy outcomes**: Link council discussions to actual development outcomes
7. **NLP enhancement**: Use named entity recognition (NER) instead of fuzzy matching

# 6. Conclusion

This study demonstrates a practical pipeline for extracting and visualizing geographic information embedded in municipal council documents. By combining OParl APIs, OpenStreetMap data, and fuzzy string matching, we create a reproducible workflow for understanding spatial dimensions of urban governance.

The resulting interactive map provides city planners, researchers, and citizens with a novel tool for analyzing where and when policy discussions occur. While this pilot analysis is limited in scope, the methodology is scalable and adaptable to other municipalities.

**Key takeaway**: Making spatial information in council records visible enables better understanding of political priorities, equity in resource allocation, and patterns in urban development discourse.

---

# 7. Technical Appendix

## 7.1 System Requirements

- **R** ≥ 4.0
- **Packages**: httr, jsonlite, dplyr, pdftools, yaml, leaflet, htmlwidgets, stringdist
- **External tools**: Pandoc (optional, for selfcontained HTML output)
- **OS**: macOS, Linux, Windows

## 7.2 Configuration (config.yaml)

```yaml
# City information
city: Augsburg
country: Deutschland

# Gazetteer settings
max_streets: 3120

# OParl API
oparl_api: "https://augsburg.de/oparl/v1.0"

# Paper download limits
max_papers: 50
max_pages_per_pdf: 50
```

## 7.3 Running the Pipeline

```bash
# Option 1: From RStudio (Open geomodelierung.Rproj first)
source("analysis/run_all.r", encoding = "UTF-8")

# Option 2: From terminal
Rscript analysis/run_all.r

# Option 3: Individual scripts
Rscript R/01_gazetteer.r
Rscript R/02_fetch_papers.r
Rscript R/03_extract_locations.r
Rscript R/04_visualize.r
```

## 7.4 Output Files

| File | Description |
|------|-------------|
| `data/gazetteer/streets.csv` | Augsburg street names with coordinates |
| `data/pdfs/*.pdf` | Downloaded council papers |
| `data/papers_metadata.csv` | Paper metadata and download info |
| `data/extracted_locations.csv` | Matched locations with scores |
| `figures/interactive_map.html` | Final visualization |

## 7.5 Troubleshooting

**Error: "FEHLER: config.yaml nicht gefunden"**
- Solution: Ensure `config.yaml` exists in project root with required fields

**Error: "Overpass API antwortet mit Status 400"**
- Solution: Check Overpass API status; try again later

**Warning: "Pandoc nicht gefunden"**
- Solution: Install with `brew install pandoc` (macOS) or use without selfcontained mode

# References

- OParl Standard: https://oparl.org/
- OpenStreetMap: https://www.openstreetmap.org/
- Overpass API: https://overpass-api.de/
- Leaflet JS: https://leafletjs.com/
- R htmlwidgets: https://www.htmlwidgets.org/
- Fuzzy String Matching: Levenshtein, V. (1966). "Binary codes capable of correcting deletions, insertions, and reversals"

---

*Last updated: `r Sys.Date()`*
*GitHub: https://github.com/Benneloui/oparl_aux_analysis*
